A Massive Molecular Gas Reservoir in the $z$\,=\,2.221 Type-2 Quasar Host Galaxy SMM\,J0939+8315 lensed by the Radio Galaxy 3C220.3

### 2016-01-13 mod1/response.md

We thank the referee for providing constructive and thoughtful
comments to improve the manuscript. We have addressed all the concerns
raised by the referee and details can be found in the revised version
-- please see attached. A brief description on how we incorporated the
changes can be found below.

# Major comments
1:
- There is already a lensing model in H14 (a paper the authors refer
  to numerous times) and it is unclear why they redid the lensing
  model (they use the same SMA data as H14 but a different code). If
  the derived model is significantly different from H14 then this
  should be highlighted otherwise the lens modeling section isn't
  necessary in this paper.

> Most parameters obtained in our new analysis with our new lensing
  code are indeed consistent with the earlier model reported by H14,
  such that the results are only modestly improved. However, H14 did
  not report the full range of best-fit parameters and uncertainties
  in their analysis, such that our results are significantly more
  detailed. To take this comment into account, we thus significantly
  shortened the text in this section by removing details on the lens
  modeling approach (and including a reference to the literature
  instead), and we have moved the lens masses and consistent results
  into Table 1 - which is used to briefly summarize the full range of
  parameters. This includes the important inferred half-light radius,
  which is used later in the analysis.

@@

2:
- The SMG is thought to harbor a luminous AGN. In that case, the LIR
  will certainly have a contribution from the AGN that should be
  accounted for otherwise the SFR will be overestimated: see
  e.g. Coppin+2010, Kirkpatrick+2012, Magdis+2013,
  Kirkpatrick+2014. Please correct LIR for the AGN emission prior to
  estimating SFR and include an AGN component in the SED fitting.

> In our analysis, we fit SED models to the rest-frame FIR, which has
  been found to have negligible AGN contribution to rest-frame FIR (≥
  60µm; Carilli+05, Netzer+07, Mullaney+11, Harrison+15). Since we do
  not have MIR measurements solely from the background SMG and due to
  the positive K correction blue-ward of dust peak, the foreground
  radio galaxy contributes a non-negligible amount to the MIR
  luminosity, we therefore didn't fit an AGN component. Including an
  additional component, and thus free parameters to the SED model will
  be over-fitted due to the limited amount of data at hand. Instead
  our SED model includes a power-law to the blue side of the dust
  peak, which accounts for the MIR excess and allows us to estimate
  the IR luminosity (Kirkpatrick+15, Riechers+13, Johnson+13,
  Casey+12). We derived the SFR and other corresponding properties
  using only L_FIR, (45-122.5µm), which is mostly due to SF-driven
  dust emission.

@@

3:
- section 4.3 is way too wordy and can be cut down to a few paragraphs
  and a table summarizing these key values (already given in Table
  4). These are all standard calculations and you can refer to CW14
  for the equations rather than repeating them here.

> We removed standard equations from the manuscript, and combined the
  sections reporting SFE, SFR, and SFRSD into one. We also shortened
  the section, as suggested.

4:
- You should also summarize the evidence for the AGN in this SMG
  (maybe when you mention this in the intro) so the reader doesn't
  have to read H14.

> We rephrased the introduction to show more clearly the evidence of
  an AGN, as suggested.

@@

5:
- [a further concern/question about Table 4 is whether all the same
  assumptions such as excitation, alpha_co, etc. were made for the
  other SMGs otherwise the comparisons are meaningless]

> We added notes in the caption of Table 4 to recap all assumptions
  used in deriving these quantities, as suggested.

@@

6:
- Section 5: why do the authors cherry-pick these 2 SMGs to make
  comparisons? there are many other sources that could be chosen with
  a range of properties. A comparison to these 2 SMGs is not useful at
  all given the diversity in this population (e.g. the sentence "This
  demonstrates the large ..." is not true when comparing only 3
  objects). I suggest comparing to the general properties observed for
  SMGs (as summarized in CW14 or Casey+14) which will be more useful
  in placing this object in the context of the SMG population.

> We took into account this comment by adding a compilation of SMG and
  type-2 QSOs properties to Table 4. Please see the table notes and
  comments for details. We have therefore included a comparison to
  these sample-averaged values in our conclusion.  We initially picked
  out two well-studied and apparently similarly bright (submillimeter
  fluxes >400 mJy) gravitationally lensed SMGs, to be able to
  investigate a broader range of physical properties - some of which
  are not as well-constrained for the broader population. Thus, we
  decided to also keep this comparison in the paper.

@@

# Minor comments
1:
- the depletion time seems short compared to other SMGs which are
  ~100Myr although maybe it is consistent with other SMGs with AGN in
  them.

> Greve+05 report a range of depletion time τ = 40-100 Myr for SMGs,
  please see also Table 4.

2:
- section headings in 3 are strange. Remove the words "New results"
  since this is obvious and a requirement for publication. Also remove
  subheading or second line in heading 3.2.

> We removed "New results" in the subject headings, as suggested.

@@

3:
- the left panels on Fig 1 and 2 should show the same region (have the
  same RA/DEC axes). It is also tough to tell by eye if the VLA9GHz
  and SMA emission is coincident. Perhaps these can be overlaid on
  Fig 1.

> We adjusted the panel sizes as suggested, and marked the locations
  of the peak emission from the SMA as white crosses on the right
  panel in Figure 1.

4:
- figure 3: orange is difficult to see. What is the SNR of the
  residuals in the right panel?

> We modified our caption to state that the quoted contour levels are
  the same for both panels in the figure. We changed the critical line
  color to green for better readability, as suggested.

@@

8: 
- SF surface density: from resolved studies of SMGs is it reasonable
  to divide half the SFR and gas mass by the area out to the
  half-light radii? give appropriate references to justify this
  assumption.

> We now provide a few citations to show that this is a common
  assumption.

9:
- intro: the first para makes it sound like our knowledge of SMGs
  comes primarily from SMGs found in large sky Herschel surveys and
  SPT but this is not true. Please include references to earlier work
  that established the basic properties of SMGs (redshift
  distribution, luminosities, SFRs, Mgas, etc) prior to Herschel even
  launching.

> We restructured the paragraph and added earlier discoveries, as
  suggested.

@@

10:
- the fact that the lensing system has two components isn't presented
  clearly in this paper. I had to read H14 to understand what the
  authors meant when they mentioned companion B. Please make this
  clearer so the reader does not have to read H14

> We added a sentence to the introduction section to elaborate on
  this, as suggested; please see the revised manuscript.

### 2016-01-13 mod1/manuscript/ms.tex
with DR's comments, re-submission to apj

\begin{document}
{\tiny  \RevisionInfo}        % place it here
\title{A Massive Molecular Gas Reservoir in the $z$\,=\,2.221 Type-2 Qruasar Host Galaxy SMM\,J0939+8315 lensed by the Radio Galaxy 3C220.3}
\author{T. K. Daisy Leung and Dominik A. Riechers}
\affil{Department of Astronomy, Space Sciences Building, Cornell University, Ithaca, NY 14853, USA; \myemail}

\begin{abstract}
We report the detection of \CO line emission in the strongly-lensed submillimeter galaxy (SMG) SMM\,J0939+8315 at $z$ = 2.221, using
the Combined Array for Research in Millimeter-wave Astronomy. 
SMM\,J0939+8315 hosts a type-2 quasar, and is gravitationally lensed by the radio galaxy 3C220.3 {\bf and its companion galaxy} at $z$ = 0.685.
The 104~GHz continuum emission underlying the CO line is detected toward 3C220.3 with an integrated flux density of $S_\textrm{cont}$ = 7.4\,$\pm$\,1.4 mJy.
Using the \CO line intensity of $I_\textrm{CO(3-2)}$ = (12.6\,$\pm$\,2.0)\,Jy\,km\,s\pmOne, we derive
 a lensing- and excitation-corrected CO line luminosity of \Lp = (3.4\,$\pm$\,0.7)\,$\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$)\,\LpU\ for the SMG, where $\mu_\textrm{L}$ is the lensing magnification factor inferred from our lens modeling.
 % performed on the 1\,mm continuum emission.
 This translates to a molecular gas mass of $M_\textrm{gas}$ = (2.7\,$\pm$\,0.6)\,$\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$)\,\Msun.
Fitting spectral energy distribution models to the (sub)-millimeter data of this SMG yields a dust temperature of $T_\textrm{dust}$ =
63.1$^{+1.1}_{-1.3}$\,K, a dust mass of $M_\textrm{dust}$ = (5.2\,$\pm$\,2.1)\,$\times$\,10$^8$\,(10.1/$\mu_\textrm{L}$)\,\Msun, and a total infrared luminosity of
$L_\textrm{IR}$ = (9.1\,$\pm$\,1.2)\,$\times$10$^{12}$\,(10.1/$\mu_\textrm{L}$)\,\Lsun.
{\bf 
We find that the properties of the interstellar medium of
 SMM J0939+8315 overlap with both SMGs and type-2 quasars. Hence, SMM J0939+8315 may be transitioning from a star-bursting phase to an unobscured quasar phase as described by the 
``evolutionary link'' model, according to which this system may represent an intermediate stage of present-day galaxies
at an earlier epoch. 
 }
\end{abstract}
\keywords{cosmology: observations --- galaxies: evolution --- galaxies: high-redshift ---  galaxies: starburst --- submillimeter: galaxies}

@@

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.80\textwidth]{f1.eps}
\caption{Left: Contour map of the 104 GHz continuum emission in the foreground radio galaxy 3C220.3.
The beam size is 12\farcs0\,$\times$\,6\farcs5, at P.A.\,=\,
$-$56$\degr$, as indicated in the bottom left corner. Right: CARMA 104 GHz continuum emission (red contours) overlaid on the VLA 9 GHz continuum emission (green contours and grayscale; H14).
The synthesized beam size of the VLA observations is 0$\farcs$6\,$\times$\,0$\farcs$2, at P.A.
76$\degr$. The contour levels of the 104 GHz continuum emission start at $\pm$2$\sigma$, incrementing at steps
of $\pm$2$\sigma$, where $\sigma$ = 0.5 mJy beam\pmOne. The contour levels of the 9 GHz continuum
emission start at $\pm$4$\sigma$, where $\sigma$\,=\,0.064 mJy beam\pmOne, and increment at steps of $\pm$2$^n\sigma$,
where $n$ is a positive integer.{\bf The blue crosses correspond to the centroid locations of the lensing knots detected in the SMA 1\,mm continuum emission (see Figure \ref{fig:mom0}).}
The central cross on each panel indicates the position of the radio core of 3C220.3. \label{fig:cont}}
\end{figure*}
\subsection{Background Galaxy: SMM\,J0939}
We detect \CO line emission at $\sim$\,8$\sigma$ significance toward the background SMG SMM\,J0939 at $z$\,=\,2.221.
The lensing-magnified spatial extent of this SMG is $\sim$\,5$\arcsec$, as shown in the Submillimeter Array (SMA) 1\,mm dust continuum image in Figure~\ref{fig:mom0} (H14); as such,
the detected \CO line emission is spatially unresolved. We therefore extract the line profile (Figure~\ref{fig:mom0}) at the peak position of the unresolved
CO emission. Fitting a four-parameter single Gaussian to the spectrum yields a peak flux density of 21.61\,$\pm$\,2.66\,\,mJy, superimposed on a
continuum level of 4.15\,$\pm$\,0.48~mJy~beam\pmOne, and a line full width at half-maximum (FWHM) of 546\,$\pm$\,36\,\,km\,\,s\pmOne.  \par
We construct a velocity-integrated (0$^\textrm{th}$ moment) map of the \CO line
emission after subtracting continuum emission in the visibility plane. This results in a velocity-integrated \CO line flux of $I_\textrm{CO}$\,=\,12.6\,$\pm$\,2.0 Jy km\,\,s\pmOne\ over a velocity range of $\Delta v$\,$\sim$\,1420 km\,\,s\pmOne, the uncertainty does not include $\sim$\,15\% calibration
uncertainty. Our \CO line measurement confirms the redshift of SMM\,J0939, yielding $z$\,=\,2.2212\,$\pm$\,0.0010.

@@

\section{Analysis}
\subsection{Lens Modelling} \label{sec:Lens}
To study the intrinsic properties of the background galaxy, we determine the magnification factor {\bf and the half-light radius of the dust region} by performing
lens modeling on the SMA 1\,mm continuum data presented by H14 of this system. 
Lens modeling is carried out in the visibility
({\it uv-}) plane using an updated version the publicly available software {\sc uvmcmcfit} \citep{uvmcmcfit15a},
details of the parametric lens model can be found in \citet{Bussmann15a}. 
{\bf The surface mass densities of the two lensing galaxies, 3C220.3 and its companion galaxy B, are described by singular isothermal ellipsoid profiles, and the source is assumed to have an
elliptical Gaussian profile. }

@@

\subsubsection{Molecular Gas Mass} \label{sec:gas}
While the ground state CO transition line traces the cold molecular gas in the ISM
\citep*[\eg][]{Wilson70a,Downes98a}, transition lines of higher rotational states ($J$ $>$ 1) are frequently observed in high-redshift sources as the
 ground state transition line is redshifted to lower frequencies that can only be observed with traditional radio telescopes
 \citep{Carilli13a}. Consequently, assumptions on the CO excitation conditions are required to derive the molecular gas mass using the $M$(H$_\textrm{2}$)-to-$L^{\prime}_\textrm{CO}$
 conversion factor ($\alpha_\mathrm{CO}$) when extrapolating from higher-$J$ CO lines. \par
{\bf Recent observations} in high-redshift quasar hosts suggest that the ratio
   is $R_\textrm{31}$\,$\sim$\,1 \citep{Riechers06a, Riechers11a}. In the case of high-redshift type-2 quasars, \citet{Riechers11a} report a brightness temperature ratio of $R_\textrm{31}$ = 1.00\,$\pm$\,0.10 for IRAS F10214+4724 (hereafter F10214), which is currently the only known type-2 quasar with both \CO and CO($J$\,=\,1\,\rarr\,0) line measurements. 
Here, we derive the molecular gas mass
assuming thermalized excitation of CO, as SMM\,J0939 is
postulated to be hosting a type-2 quasar (H14). \par
We calculate the CO($J$\,=\,1\rarr\,0) line luminosity using a standard relation
\citep[\eg][]{Solomon05a}
and assuming a conversion factor of $\alpha_\textrm{CO}$\,= 0.8\,\Msun\,(\LpU)\pmOne\ based on empirical relations from local ULIRGs, which is typically
adopted for SMGs \citep[\eg][]{Tacconi06a,Tacconi08a,Bothwell13a}.
This corresponds to \Lp = (3.42\,$\pm$\,0.71)\,$\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$) \LpU; hence the inferred total molecular gas mass is $M_\textrm{gas}$ = (2.74\,$\pm$\,0.57)\,$\times$\,\,10$^{10}$\,\Msun\, after correcting for lensing magnification. This results in a gas-to-dust
ratio of $f_\textrm{gas-dust}$\,=\,$M_\textrm{gas}/M_\textrm{dust}$\,=\,55\,$\pm$\,24. 
This is in good agreement  with the
values found in other SMGs \citep{Coppin08a,Micha10a,Riechers11c}.

@@

\subsubsection{Physical Size and Dynamical Mass}
{\bf 
Our lens model suggests a half-light radius of $r_s$\,$\sim$\,1\,kpc for the dust-emitting region in SMM\,J0939. This is comparable to the half-light radii found other SMGs with high resolution imaging. Similar sizes have been reported by \citet{Bussmann13a}, who find typical radii of 1.5 kpc for a sample of {\it Herschel}$-$selected lensed SMGs with $S_{500\micron}\,>$\,100 mJy. 
Also, \citet{Simpson15a} report a radial extent of 1.2 kpc for a sample of un-lensed SMGs with $S_{850\micron}$ = 8$-$16 mJy.}

@@

{\bf We
compare our findings for SMM\,J0939 
with a sample of typically unlensed or only weakly magnified, 850~$\micron$$-$selected SMGs \citep[][hereafter B13]{Bothwell13a}. 
Their properties are listed in Table~\ref{tab:compareSMG}, showing that SMM\,J0939 has properties similar
to other SMGs studied to date. 
The gas mass in SMM\,J0939 is slightly lower than the median in the B13 sample, but we cannot rule out the possibility that this difference is due to the different assumptions made for the gas excitation conditions. 
The gas properties (CO luminosity and gas mass) of the SMGs in the B13 sample are derived based on the assumption of typical excitation conditions found from CO spectral line energy distribution (SLED) modelling of the sample average, which the authors find them to be very similar to those of the cosmic Eyelash. Thus, we additionally compare SMM\,J0939 to two other well-studied, strongly-lensed SMGs
with comparably high apparent submillimeter fluxes
found at similar redshifts --- HLSW-01 and the cosmic Eyelash.
The properties of these sources are derived using similar approaches to those employed in this paper. 
}

@@

{\bf 
While the gas mass in SMM\,J0939 is slightly lower than the median of SMGs in the B13 sample, we find it to be consistent with other type-2 quasars, suggesting a possible scenario in which the gas has been converted into stars and used for fueling the quasar.
As such, given the presence of an obscured quasar and the overlap of properties 
with both type-2 quasar and SMG populations,
a physical interpretation might be that SMM\,J0939 is transitioning from a short, star-bursting phase to an unobscured quasar phase, consistent with the proposed evolutionary link model between dusty starbursts and quasars \citep[\eg][]{Sanders88,Coppin08a,Simpson12a}. 
}

@@

\bibitem[{{Bussmann} {et~al.}(2015{\natexlab{a}})Bussmann, Leung, \& Conley}]{uvmcmcfit15a}
Bussmann, S., Leung, T. K.~D., \& Conley, A. 2015, uvmcmcfit,
  doi:10.5281/zenodo.27357

\bibitem[{{Bussmann} {et~al.}(2015{\natexlab{b}}){Bussmann}, {Riechers}, {Fialkov},
  {Scudder}, {Hayward}, {Cowley}, {Bock}, {Calanog}, {Chapman}, {Cooray}, {De
  Bernardis}, {Farrah}, {Fu}, {Gavazzi}, {Hopwood}, {Ivison}, {Jarvis},
  {Lacey}, {Loeb}, {Oliver}, {Perez-Fournon}, {Rigopoulou}, {Roseboom},
  {Scott}, {Smith}, {Vieira}, {Wang}, \& {Wardlow}}]{Bussmann15a}
{Bussmann}, R.~S., {Riechers}, D., {Fialkov}, A., {et~al.} 2015, ArXiv
  e-prints, arXiv:1504.05256

>>>>

\begin{document}
{\tiny  \RevisionInfo}        % place it here
\title{A Massive Molecular Gas Reservoir in the $z$\,=\,2.221 Type-2 Quasar Host Galaxy SMM\,J0939+8315 lensed by the Radio Galaxy 3C220.3}
\author{T. K. Daisy Leung and Dominik A. Riechers}
\affil{Department of Astronomy, Space Sciences Building, Cornell University, Ithaca, NY 14853, USA; \myemail}

\begin{abstract}
We report the detection of \CO line emission in the strongly-lensed submillimeter galaxy (SMG) SMM\,J0939+8315 at $z$ = 2.221, using
the Combined Array for Research in Millimeter-wave Astronomy. 
SMM\,J0939+8315 hosts a type-2 quasar, and is gravitationally lensed by the radio galaxy 3C220.3 {\bf and its companion galaxy} at $z$ = 0.685.
The 104~GHz continuum emission underlying the CO line is detected toward 3C220.3 with an integrated flux density of $S_\textrm{cont}$ = 7.4\,$\pm$\,1.4 mJy.
Using the \CO line intensity of $I_\textrm{CO(3-2)}$ = (12.6\,$\pm$\,2.0)\,Jy\,km\,s\pmOne, we derive
 a lensing- and excitation-corrected CO line luminosity of \Lp = (3.4\,$\pm$\,0.7)\,$\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$)\,\LpU\ for the SMG, where $\mu_\textrm{L}$ is the lensing magnification factor inferred from our lens modeling.
 This translates to a molecular gas mass of $M_\textrm{gas}$ = (2.7\,$\pm$\,0.6)\,$\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$)\,\Msun.
Fitting spectral energy distribution models to the (sub)-millimeter data of this SMG yields a dust temperature of $T$\,=\,63.1$^{+1.1}_{-1.3}$\,K, a dust mass of $M_\textrm{dust}$ = (5.2\,$\pm$\,2.1)\,$\times$\,10$^8$\,(10.1/$\mu_\textrm{L}$)\,\Msun, and a total infrared luminosity of
$L_\textrm{IR}$ = (9.1\,$\pm$\,1.2)\,$\times$10$^{12}$\,(10.1/$\mu_\textrm{L}$)\,\Lsun.
{\bf 
We find that the properties of the interstellar medium of
 SMM J0939+8315 overlap with both SMGs and type-2 quasars. Hence, SMM J0939+8315 may be transitioning from a star-bursting phase to an unobscured quasar phase as described by the 
``evolutionary link'' model, according to which this system may represent an intermediate stage in the evolution of present-day galaxies
at an earlier epoch. 
 }
\end{abstract}
\keywords{cosmology: observations --- galaxies: evolution --- galaxies: high-redshift ---  galaxies: starburst --- submillimeter: galaxies}

@@

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.80\textwidth]{f1.eps}
\caption{Left: Contour map of the 104 GHz continuum emission in the foreground radio galaxy 3C220.3.
The beam size is 12\farcs0\,$\times$\,6\farcs5, at P.A.\,=\,
$-$56$\degr$, as indicated in the bottom left corner. Right: CARMA 104 GHz continuum emission (red contours) overlaid on the VLA 9 GHz continuum emission (green contours and grayscale; H14).
The synthesized beam size of the VLA observations is 0$\farcs$6\,$\times$\,0$\farcs$2, at P.A.
76$\degr$. The contour levels of the 104 GHz continuum emission start at $\pm$2$\sigma$, incrementing at steps
of $\pm$2$\sigma$, where $\sigma$ = 0.5 mJy beam\pmOne. The contour levels of the 9 GHz continuum
emission start at $\pm$4$\sigma$, where $\sigma$\,=\,0.064 mJy beam\pmOne, and increment at steps of $\pm$2$^n\sigma$,
where $n$ is a positive integer. {\bf The blue crosses correspond to the centroid locations of the lensing knots detected in the SMA 1\,mm continuum emission (see Figure \ref{fig:mom0}).}
The central cross on each panel indicates the position of the radio core of 3C220.3. \label{fig:cont}}
\end{figure*}
\subsection{Background Galaxy: SMM\,J0939}
We detect \CO line emission at $\sim$\,8$\sigma$ significance toward the background SMG SMM\,J0939 at $z$\,=\,2.221.
The lensing-magnified spatial extent of this SMG is $\sim$\,5$\arcsec$, as shown in the Submillimeter Array (SMA) 1\,mm dust continuum image in Figure~\ref{fig:mom0} (H14); as such,
the detected \CO line emission is spatially unresolved. We therefore extract the line profile (Figure~\ref{fig:mom0}) at the peak position of the unresolved
CO emission. Fitting a four-parameter single Gaussian to the spectrum yields a peak flux density of 21.61\,$\pm$\,2.66\,\,mJy, superimposed on a
continuum level of 4.15\,$\pm$\,0.48~mJy~beam\pmOne, and a line full width at half-maximum (FWHM) of 546\,$\pm$\,36\,\,km\,\,s\pmOne.  \par
We construct a velocity-integrated (0$^\textrm{th}$ moment) map of the \CO line
emission after subtracting continuum emission in the visibility plane. This results in a velocity-integrated \CO line flux of $I_\textrm{CO}$\,=\,12.6\,$\pm$\,2.0 Jy km\,\,s\pmOne\ over a velocity range of $\Delta v$\,$\sim$\,1420 km\,\,s\pmOne, the uncertainty does not include $\sim$\,15\% calibration
uncertainty. Our \CO line measurement confirms the redshift of SMM\,J0939, yielding $z$\,=\,2.2212\,$\pm$\,0.0010.

@@

\section{Analysis}
\subsection{Lens Modelling} \label{sec:Lens}
To study the intrinsic properties of the background galaxy, we determine the magnification factor {\bf and the half-light radius of the dust region} by performing
lens modeling on the SMA 1\,mm continuum data presented by H14 of this system. 
Lens modeling is carried out in the visibility
({\it uv-}) plane using an updated version of the publicly available software {\sc uvmcmcfit} \citep{uvmcmcfit15a},
details of the parametric lens model can be found in \citet{Bussmann15a}. 
{\bf The surface mass densities of the two lensing galaxies, 3C220.3 and its companion galaxy B, are described by singular isothermal ellipsoid profiles, and the source is assumed to have an
elliptical Gaussian profile. }

@@

\subsubsection{Molecular Gas Mass} \label{sec:gas}
While the ground state CO transition line traces the cold molecular gas in the ISM
\citep*[\eg][]{Wilson70a,Downes98a}, transition lines of higher rotational states ($J$ $>$ 1) are frequently observed in high-redshift sources as the
 ground state transition line is redshifted to lower frequencies that can only be observed with traditional radio telescopes
 \citep{Carilli13a}. Consequently, assumptions on the CO excitation conditions are required to derive the molecular gas mass using the $M$(H$_\textrm{2}$)-to-$L^{\prime}_\textrm{CO}$
 conversion factor ($\alpha_\mathrm{CO}$) when extrapolating from higher-$J$ CO lines. \par
{\bf Recent observations} in high-redshift quasar hosts suggest that the ratio
   is $R_\textrm{31}$\,$\sim$\,1 \citep{Riechers06a, Riechers11a}. In the case of high-redshift type-2 quasars, \citet{Riechers11a} report a brightness temperature ratio of $R_\textrm{31}$ = 1.00\,$\pm$\,0.10 for IRAS F10214+4724 (hereafter F10214), which is currently the only known type-2 quasar with both \CO and CO($J$\,=\,1\,\rarr\,0) line measurements. 
Here, we derive the molecular gas mass
assuming thermalized excitation of CO, as SMM\,J0939 is
postulated to be hosting a type-2 quasar (H14). \par
We calculate the CO($J$\,=\,1\rarr\,0) line luminosity using a standard relation
\citep[\eg][]{Solomon05a}
and assuming a conversion factor of $\alpha_\textrm{CO}$\,= 0.8\,\Msun\,(\LpU)\pmOne\ based on empirical relations from local ULIRGs, which is typically
adopted for SMGs \citep[\eg][]{Tacconi06a,Tacconi08a,Bothwell13a}.
This corresponds to \Lp = (3.42\,$\pm$\,0.71)\,$\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$) \LpU; hence the inferred total molecular gas mass is $M_\textrm{gas}$ = (2.74\,$\pm$\,0.57)\,$\times$\,\,10$^{10}$\,\Msun\, after correcting for lensing magnification. This results in a gas-to-dust
ratio of $f_\textrm{gas-dust}$\,=\,$M_\textrm{gas}/M_\textrm{dust}$\,=\,55\,$\pm$\,24. 
This is in good agreement  with the
values found for other SMGs \citep{Coppin08a,Micha10a,Riechers11c}.

@@

\subsubsection{Physical Size and Dynamical Mass}
{\bf 
Our lens model suggests a half-light radius of $r_s$\,$\sim$\,1\,kpc for the dust-emitting region in SMM\,J0939. This is comparable to the half-light radii found in other SMGs with high resolution imaging. Similar sizes have been reported by \citet{Bussmann13a}, who find typical radii of 1.5 kpc for a sample of {\it Herschel}$-$selected lensed SMGs with $S_{500\micron}\,>$\,100 mJy. 
Also, \citet{Simpson15a} report a radial extent of 1.2 kpc for a sample of un-lensed SMGs with $S_{850\micron}$ = 8$-$16 mJy.}

@@

{\bf We
compare our findings for SMM\,J0939 
with a sample of typically unlensed or only weakly magnified, 850~$\micron$$-$selected SMGs \citep[][hereafter B13]{Bothwell13a}. 
Their properties are listed in Table~\ref{tab:compareSMG}, showing that SMM\,J0939 has properties similar
to other SMGs studied to date. 
The gas mass in SMM\,J0939 is slightly lower than the median in the B13 sample, but we cannot rule out the possibility that this difference is due to the different assumptions made for the gas excitation conditions. 
The gas properties (CO luminosity and gas mass) of the SMGs in the B13 sample are derived based on the assumption of typical excitation conditions found from CO spectral line energy distribution (SLED) modelling of the sample average, which the authors find to be very similar to those of the cosmic Eyelash. Thus, we additionally compare SMM\,J0939 in more detail to two other well-studied, strongly-lensed SMGs
with comparably high apparent submillimeter fluxes
found at similar redshifts --- HLSW-01 and the cosmic Eyelash.
The properties of these sources are derived using similar approaches to those employed in this paper. 
}

@@

{\bf 
While the gas mass in SMM\,J0939 is slightly lower than the median of SMGs in the B13 sample, we find it to be consistent with other type-2 quasars, suggesting a possible scenario in which a significant fraction of the gas has already been converted into stars and used for fueling the quasar.
As such, given the presence of an obscured quasar and the overlap of properties 
with both type-2 quasar and SMG populations,
a physical interpretation might be that SMM\,J0939 is transitioning from a short, star-bursting phase to an unobscured quasar phase, consistent with the proposed evolutionary link model between dusty starbursts and quasars \citep[\eg][]{Sanders88,Coppin08a,Simpson12a}. 
}

@@

\bibitem[{{Bussmann} {et~al.}(2015{\natexlab{a}})Bussmann, Leung, \& Conley}]{uvmcmcfit15a}
Bussmann, S., Leung, T. K.~D., \& Conley, A. 2015{\natexlab{a}}, uvmcmcfit,
  doi:10.5281/zenodo.27357

\bibitem[{{Bussmann} {et~al.}(2015{\natexlab{b}}){Bussmann}, {Riechers}, {Fialkov},
  {Scudder}, {Hayward}, {Cowley}, {Bock}, {Calanog}, {Chapman}, {Cooray}, {De
  Bernardis}, {Farrah}, {Fu}, {Gavazzi}, {Hopwood}, {Ivison}, {Jarvis},
  {Lacey}, {Loeb}, {Oliver}, {P{\'e}rez-Fournon}, {Rigopoulou}, {Roseboom},
  {Scott}, {Smith}, {Vieira}, {Wang}, \& {Wardlow}}]{Bussmann15a}
{Bussmann}, R.~S., {Riechers}, D., {Fialkov}, A., {et~al.} 2015{\natexlab{b}}, \apj, 812, 43
